\TheTitle

### 2016-07-25 linvis.tex
added a minor clarification

\begin{itemize}
\item 5 merges were false-erros because their logs did not contain accurate information (were probably edited by
  hand). For example in \mycode{42a579a0f...}) one commit summary was missing (the line was empty), in another  \mycode
  {c55d267}) the summaries were reordered.
\item The heuristic works correctly for all merges except between Jun 7, 2014 and Jun 2, 2014 (92 merges) and before
  Sept 4, 2007. Before this date merges did not include a summary of the commits they included, hence making it
  impossible to verify; however, we correctly identified the merges by Linus into master. 
\item Before Dec. 12, 2006 (1542 merges) our heuristic breaks due to the
presence of \textit{foxtrot} commits, which confound the true master branch of a
repository
\footnote{See \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a description of the issue}, and
is not capable of identifying most of the merges before this date.
\end{itemize}

>>>>

\begin{itemize}
\item 5 merges were false-erros because their logs did not contain accurate information (were probably edited by
  hand). For example in \mycode{42a579a0f...}) one commit summary was missing (the line was empty), in another  \mycode
  {c55d267}) the summaries were reordered.
\item The heuristic works correctly for all merges except between Jun 7, 2014 and Jun 2, 2014 (92 merges) and before
  Sept 4, 2007. Before this date, and until Dec 12, 2006, merges did not include a summary of the commits they included, hence making it
  impossible to verify; however, we correctly identified the merges by Linus into master. 
\item Before Dec. 12, 2006 (1542 merges) our heuristic breaks due to the
presence of a \textit{foxtrot} commit (\mycode{c436688...}), which confounded the true master branch of a
repository
\footnote{See \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a description of the issue}, and
is not capable of identifying most of the merges before this date.
\end{itemize}
